\hypertarget{the-pirate-ipsum-theorem}{%
\section{\texorpdfstring{The \emph{Pirate ipsum}
Theorem}{The Pirate ipsum Theorem}}\label{the-pirate-ipsum-theorem}}

{\begin{lemma}

Chase guns doubloon crimp rutters barkadeer gunwalls weigh anchor Plate
Fleet lookout brigantine. Log gunwalls bucko matey hands crow's nest
haul wind walk the plank swing the lead ballast. Lugger American Main
coffer topmast topsail jib lookout topgallant dance the hempen jig
interloper.

\end{lemma}}

{\begin{lemma}

Chase bilged on her anchor measured fer yer chains overhaul chandler
loaded to the gunwalls nipperkin coffer Plate Fleet mutiny.

\end{lemma}}

{\begin{theorem}[Pirate ipsum]

Cog pinnace broadside crack Jennys tea cup scourge of the seven seas
knave me Arr yardarm Davy Jones' Locker. Fore league cutlass shrouds six
pounders gun bilge rat lookout code of conduct pillage.

\end{theorem}}

\hypertarget{the-variant-by-benjamin-hornigold}{%
\section{The variant by Benjamin
Hornigold}\label{the-variant-by-benjamin-hornigold}}

{\renewcommand{\thetheorem}{3.1.5}\begin{theorem}[Pirate ipsum by
Hornigold (1680)]

Crow's nest marooned Yellow Jack cutlass code of conduct rope's end
belay mizzenmast Spanish Main yard. Carouser broadside cog careen tender
wherry provost Arr red ensign chase guns. Strike colors furl man-of-war
keelhaul smartly dead men tell no tales red ensign crow's nest walk the
plank long clothes.

\end{theorem}\addtocounter{theorem}{-1}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-BenjaminHornigold}{}}%
Hornigold, Benjamin. 1680. \emph{A Proof of Pirate Ipsum}.

\end{CSLReferences}
